\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2021-02-21 popl-2019-journal-v/discussion.tex
Fix final reviewer comments.

\begin{jversion}
  A compiler is secure when it enforces the properties of high-level languages which begs the question what properties we should enforce.
  When it comes to fully-abstract compilation, then the answer is that all properties in the
  high-level language should be enforced (or at least the equivalences they imply), so the real question is what high-level language we would like.
  \stktokens{} ensures a standard call-return control-flow, but if we want a different kind of control-flow, for instance call/cc or C's \texttt{longjmp}, then we need to come up with a different enforcement scheme.
  Further, many high-level languages have exceptions as another form of control-flow not (yet) supported by \stktokens{}.
  This goes to show how we must consider what high-level language we want in order to answer the question of what properties we must enforce to get a fully-abstract compiler.
  % Lau: Say something about address hiding?

>>>>

\begin{jversion}
  A compiler is secure when it enforces the properties of high-level languages which begs the question what properties we should enforce.
  When it comes to fully-abstract compilation, then the answer is that all properties in the high-level language (or at least the equivalences they imply\footnote{See Section~\ref{sec:related-work} for a discussion of secure compilation properties that require preservation of more general language properties than equivalences.}) must be preserved in the target language, either by translating them to similar abstractions in the target language or by using the available target language features to enforce the source language abstraction.
  In our case, \srccm{} semantics offers a native stack with LSE and WBCF, but this abstraction does not natively exist in \trgcm{}, so \stktokens{} can be used to enforce it.

  Perhaps a more subjective question is what kind of high-level language we would like.
  \stktokens{} ensures a standard call-return control-flow, but if we want a different kind of control-flow, for instance call/cc or C's \texttt{longjmp}, then we need to come up with a different enforcement scheme.
  Further, many high-level languages have exceptions as another form of control-flow not (yet) supported by \stktokens{}.
  This goes to show how we must consider what high-level language we want in order to answer the question of what properties we must enforce to get a fully-abstract compiler.
  % Lau: Say something about address hiding?

### 2021-02-21 popl-2019-journal-v/paper.tex
Fix final reviewer comments.

\section{A Capability Machine with Sealing and Linear Capabilities}
\label{sec:cap-mach-w-seal-and-lin}
% Brief intro to section and this cap machine:
% Cap machine inspired by CHERI, but with linear capabilities
In this section, we introduce a simple but representative capability machine with linear capabilities, that we call \trgcm{} (Linear Capability Machine).
\trgcm{} is mainly inspired by CHERI~\citep{watson_cheri_2015} with linear capabilities as the main addition.
For simplicity, \trgcm{} assumes an infinite address space and unbounded integers.\footnote{Although we have not thoroughly investigated, we do not believe our results depend heavily on these assumptions and we expect they could be lifted without a great impact on the proofs.}
% \lau{Do we have a good reason to assume an infinite address space for this work?
%   We do not model malloc, so we do not need to worry about what happens when malloc runs out of memory.}

@@

% Back to high-level view
As discussed earlier, our formal results only provide guarantees for components that respect the calling convention.
Untrusted components are not assumed to do so.
To formalize this distinction, \srccm{} has a set of trusted addresses $\ta$.
This $\ta$ is a constant parameter of the \srccm{} step relation.
Only instructions at these addresses will be interpreted as native \srccm{} calls and push frames to the call stack.
As such, WBCF and LSE for calls from these addresses.
In addition to $\ta{}$, \stktokens{} assumes a fixed base address of the stack memory, that is also passed around as such a parameter, for use in the native semantics of calls.

>>>>

\section{A Capability Machine with Sealing and Linear Capabilities}
\label{sec:cap-mach-w-seal-and-lin}
% Brief intro to section and this cap machine:
% Cap machine inspired by CHERI, but with linear capabilities
In this section, we introduce a simple but representative capability machine with linear capabilities, which we call \trgcm{} (Linear Capability Machine).
\trgcm{} is mainly inspired by CHERI~\citep{watson_cheri_2015} with linear capabilities as the main addition.
For simplicity, \trgcm{} assumes an infinite address space and unbounded integers.\footnote{Although we have not thoroughly investigated, we do not believe our results depend heavily on these assumptions and we expect they could be lifted without a great impact on the proofs.}
% \lau{Do we have a good reason to assume an infinite address space for this work?
%   We do not model malloc, so we do not need to worry about what happens when malloc runs out of memory.}

@@

% Back to high-level view
As discussed earlier, our formal results only provide guarantees for components that respect the calling convention.
Untrusted components are not assumed to do so.
To formalize this distinction, \srccm{} has a set of trusted addresses $\ta$.
This $\ta$ is a constant parameter of the \srccm{} step relation.
Only instructions at these addresses will be interpreted as native \srccm{} calls and push frames to the call stack.
As such, WBCF and LSE will be guaranteed only for calls from these addresses.
In addition to $\ta{}$, \stktokens{} assumes a fixed base address of the stack memory, that is also passed around as such a parameter, for use in the native semantics of calls.
